Learning Auditory Similarities Between Instrumental Playing Techniques

### 2019-10-31 paper/paper.tex
update integer ranges for n and q

For a given reference clustering $D_k$, the p@5 is computed as follows.
For each sound $s_q, 0<q<9346$ considered as a query, its 5 nearest neighbors $s_n, 0<n<5$ in the timbre space under evaluation are retrieved using the Euclidean distance between corresponding features vectors.
For this query, the precision is defined as:
$$
p@5_q = \frac{1}{5} \sum_{n=1}^5 \mathbf{1}_{D_q=D_n}
$$
The p@5 is the average $p@5_q$ computed over all queries.
\ja{This is perhaps better described in reverse, starting with $p@5_q$, then $p@5$, then $ap@5$?
Also, we define the precisions here as proportions (between zero and one), but later, we present them as percentages (between $0\%$ and $100\%$).}%

>>>>

For a given reference clustering $D_k$, the p@5 is computed as follows.
For each sound $s_q, 0<q\leq9346$ considered as a query, its 5 nearest neighbors $s_n, 0<n\leq5$ in the timbre space under evaluation are retrieved using the Euclidean distance between corresponding features vectors.
For this query, the precision is defined as:
$$
p@5_q = \frac{1}{5} \sum_{n=1}^5 \mathbf{1}_{D_q=D_n}
$$
The p@5 is the average $p@5_q$ computed over all queries.
\ja{This is perhaps better described in reverse, starting with $p@5_q$, then $p@5$, then $ap@5$?
Also, we define the precisions here as proportions (between zero and one), but later, we present them as percentages (between $0\%$ and $100\%$).}%
